### 2023-09-26 paper/draft.tex
AURC update for meeting 26/09
making sanity check
Updates from Overleaf

\section{Example \AURC}

@@

For \DC{}, we benchmark results on both \tobacco{} (original train-val-test splits 800-200-2482) and \rvl.  
We also created a subsampled student training set, \rvlone, by randomly selecting 1K training images per class from \rvl. The originally large training size hinders experimentation (longer iteration cycles).
By evaluating the full \rvl{} test set, we provide a fair evaluation of the usefulness of KD methods, while avoiding the cumbersomeness of student fine-tuning on a large dataset. Additionally, we evaluate on RVL-CDIP-N, which is a test set created for testing robustness to covariate shifts.

@@

>>>>

\section*{Updates 27/09}

\begin{itemize} %tailor to audience
    \item $f(x)_{k+1}$: write out with $g$, as it is restrictive to have this additional output in $[0,1]$, can be in $\mathbb{R}$; can have its own parameters and features
    \item Sanity check complete
    \item Differentiability: 1) indicator function, 2) comparison (>)
\end{itemize}

% \section{Example \AURC}

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=0.5\textwidth]{figures/aurc_example.png}
%     \caption{Example of \AURC{} calculation for a 3-class problem with a reject option.}
%     \label{fig:aurc_example}
% \end{figure}

@@

For \DC{}, we benchmark results on both \tobacco{} (original train-val-test splits 800-200-2482) and \rvl.  
We also created a subsampled student training set, \rvlone, by randomly selecting 1K training images per class from \rvl. The originally large training size hinders experimentation (longer iteration cycles).
By evaluating the full \rvl{} test set, we provide a fair evaluation of the usefulness of KD methods, while avoiding the cumbersomeness of student fine-tuning on a large dataset. Additionally, we evaluate RVL-CDIP-N, which is a test set created for testing robustness to covariate shifts.

@@

% Considering standard Neural Networks (NNs), the last layer outputs a vector of real-valued \textit{logits} $\mathbf{z} \in \mathbb{R}^K$, which in turn are normalized using a sigmoid/softmax activation function.

% $\displaystyle \sigma(z) = \frac{1}{1 + \exp^{-z}}$
% $\displaystyle \text{softmax}(\mathbf{z}) = \frac{{\exp(z)}}{{\sum_{k=1}^{K} \exp(z_k)}}$

% For convenience, $f_{k}(x)$ denotes the $k$-th element of the output vector.

% $\hat{y} = \argmax_{y'\in{\mathcal{Y}}}f_{y'}(X)$ is the top-1 class prediction

% $\hat{p}= \max_{y'\in{\mathcal{Y}}}f_{y '}(X)$ is the associated posterior probability
% Some interesting distributions are defined:

% \begin{itemize}
%     \item $\mathcal{D}_{\text {in }}$ denotes the distribution over $\mathcal{X}$ of in-distribution (ID) data
%     \item 	 $\mathcal{D}_{\text {in }}^{\text {test }, \checkmark}$ and $\mathcal{D}_{\text {in }}^{\text {test }, \times}$ represent the distribution of correct and misclassified ID test samples
% \end{itemize}

% Now to combine these two measures into a single metric, we need to define a trade-off between risk and coverage. This is done by defining a \textit{cost} function $c(\cdot)$, which is a function of the risk and coverage. The cost function is defined as the weighted sum of the risk and coverage, where the weights are defined by the user. The cost function is defined as:
% \begin{equation}
%     c(\mathcal{R}_{\tau}(f, g), \mathcal{C}_{\tau}(f, g))=\alpha \mathcal{R}_{\tau}(f, g)+(1-\alpha) \mathcal{C}_{\tau}(f, g)
% where $\alpha \in[0,1]$ is a user-defined parameter that controls the trade-off between risk and coverage. The cost function is a function of the threshold $\tau$ and the selector $g$.
